<<<<<<< HEAD
---
title: "Dominant Resident males cooperate with Satellites to limit their losses"
author: "Belojevic et al."
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Codes for statistical analysis ###

## MS structure

I. Non-social predictors

II. Between Resident differences with a Satellite on the lek 

III. Within-Resident differences between the Satellite and Control conditions 
  


### Packages

```{r packages}

library(lme4)
library(lmtest)
library(MASS)
library(glmmTMB)
library(performance)
library(rstanarm)
library(brms)  # for models
library(bayesplot)
library(ggplot2)
library(dplyr)
library(tidybayes)
library(modelr)
library(pscl)
library(GLMMadaptive)
library(fitdistrplus)
library(AER)
library(tidyr)
library(car)
library(AICcmodavg)
library(VGAM) # tobit function
library(DHARMa)
library(readxl)
library(stringr)
library(sjPlot) # ploy_model
library(scales)
library(emmeans)
library(patchwork)
library(data.table)
library(DHARMa)
library(sjPlot)

```



##### Data analysis #####

### Preparing data files

```{r Data sets}

# Only Resident behaviour data set
Session_behav_all_res <- read.csv("Session_behav_no_state_aggression.csv")

```


### I. Non-social predictors of female receptivity

# Female baseline data set proeparation

Identifying variables that influences female visits and copulations over the season. Keep the ones with an effect for the later tests as covariants.


```{r Non-social predictors data set prep}

Session_behav_df <- read.csv("Resident cooperation MS Kupan Data/session_behav_df_full.csv")

# Merging data across sessions
Female_baseline <- Session_behav_df %>% group_by(Session_ID, Video_ID, Condition, Fm_ID, Time, Date, Date2, Week, Combo_lek_week, Combo_lek) %>% 
  summarize(across(c(Female_max_id, Female_max_id, Total_visit_duration_all_females, Total_visit_nr_all_females, Total_nr_display, Total_nr_display_with_Sat, Total_nr_display_Res_ind, Total_nr_display_Sat_ind, Female_cop_max_id, Interrupted_copulations_nr_OtherR, Interrupted_copulations_nr_OtherS, Interrupted_copulations_nr_PartnerR, Interrupted_copulations_nr_PartnerS, Successful_copulations_nr, Interrupted_total,Female_mount_max_id, Mount_nr, Female_max_crouching_id, Crouching_nr, Copulation_attempt,Copulation_nr, Total_successful_copulations, Total_copulation_nr, Co.display_total_nr_session, Co.display_total_duration_s_session, Aggression_total, Fight_dur_s), \(x) sum(x, na.rm = TRUE)), across(c(Total_copulation_occurrence, Copulation_occurrence),  \(x) mean(x, na.rm = TRUE)))

Female_baseline$Total_copulation_occurrence <- ifelse(Female_baseline$Total_copulation_occurrence > 0, 1, Female_baseline$Total_copulation_occurrence)

Female_baseline$Copulation_occurrence <- ifelse(Female_baseline$Copulation_occurrence > 0, 1, Female_baseline$Copulation_occurrence)


```


## I/a. Total number of female visits


```{r Visit number models}

### Occurrence of female visits in a session (0/1)

Female_baseline$Visit_occurrence <- ifelse(Female_baseline$Total_visit_nr_all_females > 0, 1, 0)


### Visit numbers

sum(Female_baseline$Total_visit_nr_all_females) # 733

sum(Female_baseline$Total_visit_nr_all_females[Female_baseline$Fm_ID == "Fm1"]) # 141

sum(Female_baseline$Total_visit_nr_all_females[Female_baseline$Fm_ID == "Fm2"]) # 592


# Gaussian
fm_vis_bl_lm_model1 <- glmmTMB(Total_visit_nr_all_females ~Date2 +  Fm_ID + Time, data = Female_baseline)
summary(fm_vis_bl_lm_model1)

# Neg bin
fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = nbinom2)
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
performance::check_overdispersion(fm_vis_bl_nb_model1)
performance::check_singularity(fm_vis_bl_nb_model1, tol = 1e-05)
# Zero inflated


# Poisson
fm_vis_bl_poi_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = poisson(link = "log"))
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
performance::check_overdispersion(fm_vis_bl_nb_model1)
# zero inflated, over dispersed


# Zero-inflated neg bin
fm_vis_bl_zinb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2+  Fm_ID + Time + Total_nr_display, data = Female_baseline,  family = nbinom2, zi = ~ 1 ) 
summary(fm_vis_bl_zinb_model1)
performance::check_zeroinflation(fm_vis_bl_zinb_model1, tolerance = 0.05)
performance::check_overdispersion(fm_vis_bl_zinb_model1)
# Zero-inflated


# Zero-inflated neg bin full model
fm_vis_bl_zinb_model2 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = nbinom2, zi = ~ 1 + Date2 + Fm_ID + Time) 
summary(fm_vis_bl_zinb_model2)
performance::check_zeroinflation(fm_vis_bl_zinb_model2, tolerance = 0.05)
performance::check_overdispersion(fm_vis_bl_zinb_model2)
confint(fm_vis_bl_zinb_model2, level = 0.95, method = "profile")
# Ok - best model fit

anova(fm_vis_bl_zinb_model2, fm_vis_bl_zinb_model1, fm_vis_bl_nb_model1)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = fm_vis_bl_zinb_model2)

# Plot residuals
plot(sim_res)
# There is sign of some uncaptured variance in the model but otherwise it's acceptable

## https://stats.stackexchange.com/questions/548478/how-to-interpret-meaning-of-residual-vs-predicted-quantile-plots-in-dharma

plot_model(fm_vis_bl_zinb_model2, type = "pred", terms = "Date2")
plot_model(fm_vis_bl_zinb_model2, type = "pred", terms = "Fm_ID")
plot_model(fm_vis_bl_zinb_model2, type = "pred", terms = "Time")

```


## I/b. Total duration of female visits


```{r Visit duartion models}

## Data distribution test

hist(Female_baseline$Total_visit_duration_all_females)

# Remove 0 values and test

Female_baseline2 <- Female_baseline[Female_baseline$Total_visit_duration_all_females >= 1,]

hist(Female_baseline2$Total_visit_duration_all_females)


# Testing distribution on all values

plotdist(log(Female_baseline2$Total_visit_duration_all_females), histo = TRUE, demp = TRUE)

fn <- fitdist(Female_baseline$Total_visit_duration_all_females, "norm")
summary(fn)
plot(fn)

fn <- fitdist(Female_baseline2$Total_visit_duration_all_females, "norm")
summary(fn)
plot(fn)
# Okayish


# Testing distribution of non-zero values

plotdist(Female_baseline2$Total_visit_duration_all_females, histo = TRUE, demp = TRUE)

descdist(Female_baseline2$Total_visit_duration_all_females, boot = 1000)
# It fits really horribly to normal without transformation

descdist(log(Female_baseline2$Total_visit_duration_all_females), boot = 1000)
# Better


# Log-transforming non-zero values and test distribution

Female_baseline$Total_visit_duration_all_females_tr <- ifelse(Female_baseline$Total_visit_duration_all_females == 0, 0, log(Female_baseline$Total_visit_duration_all_females))

hist(Female_baseline$Total_visit_duration_all_females_tr)

fn_tr <- fitdist(Female_baseline$Total_visit_duration_all_females_tr, "norm")
summary(fn_tr)
plot(fn_tr)
# log transformed non-zero values look nicely normally distributed


## Models

# Decide whether normal, Tobit or hurdle model is better? Tobit and Hurdle give the same results


## Hurdle models 

# basic ln model
visit_norm_m <- lm(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + Time, data=Female_baseline)
summary(visit_norm_m)


# Hurdle log-norm model on transformed data
visit_lognorm_hurdle_m_tr <- glmmTMB(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + Time, data=Female_baseline, family = glmmTMB::lognormal(link ="log"), ziformula = ~ 1+ Date2 + Fm_ID + Time)
summary(visit_lognorm_hurdle_m_tr)


# Hurdle gamma model on transformed data
visit_gamma_hurdle_m_tr <- glmmTMB(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + Time, data=Female_baseline, family = glmmTMB::ziGamma(link="log"), ziformula = ~ 1 + Date2 + Fm_ID + Time)
summary(visit_gamma_hurdle_m_tr)
confint(visit_gamma_hurdle_m_tr, level = 0.95, method = "profile")
# Best model fit - final model

anova(visit_lognorm_hurdle_m_tr, visit_gamma_hurdle_m_tr)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = visit_gamma_hurdle_m_tr)

# Plot residuals
plot(sim_res)
# There is sign of some uncaptured variance in the model but otherwise it's acceptable

testDispersion(sim_res)
# Ok

plotResiduals(sim_res, form = visit_lognorm_hurdle_m_tr$Date2)

plotResiduals(sim_res, form = visit_lognorm_hurdle_m_tr$Fm_ID)

plotResiduals(sim_res, form = visit_lognorm_hurdle_m_tr$Time)

```


## I/c. Number of copulation attempts


```{r Copulation attempts models}


## Date distribution tests

#Total copulation attempts in sat and res conditions - all interrupted and successful copulations together

# Copulations - using "Total_copulation_nr" for a male that is the total number of successful and interrupted copulations for a session for a male - here I use total cop number because I test the female willingness to copulate and not the actual success

hist(Female_baseline$Total_copulation_nr)

sum(Female_baseline$Copulation_nr) # 286

sum(Female_baseline[Female_baseline$Condition == "Satellite",]$Copulation_nr) # 142 with satellite copulations

sum(Female_baseline[Female_baseline$Condition == "Marginal",]$Copulation_nr) # 144

# Copulations by female compartments

sum(Female_baseline$Copulation_nr[Female_baseline$Fm_ID == "Fm1"]) # 134

sum(Female_baseline$Copulation_nr[Female_baseline$Fm_ID == "Fm2"]) # 152


## Copulation attempt models


# Gaussian - preliminary analysis
fm_cop_bl_lm_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, data = Female_baseline)
summary(fm_cop_bl_lm_model1)

# Neg bin
fm_cop_bl_nb_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, data = Female_baseline, family = nbinom2)
summary(fm_cop_bl_nb_model1)
performance::check_zeroinflation(fm_cop_bl_nb_model1, tolerance = 0.05)
performance::check_overdispersion(fm_cop_bl_nb_model1)
# Ok

fm_cop_bl_poi_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, family = poisson(link="log"), data = Female_baseline)
summary(fm_cop_bl_poi_model1)
performance::check_zeroinflation(fm_cop_bl_poi_model1, tolerance = 0.05)
performance::check_overdispersion(fm_cop_bl_poi_model1)
# Zero inflated, over dispersed

# Zero-infalted neg bin
fm_cop_bl_zi_nb_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time,, data = Female_baseline, family = nbinom2, zi = ~ Date2 + Fm_ID + Time)
summary(fm_cop_bl_zi_nb_model1)
performance::check_zeroinflation(fm_cop_bl_zi_nb_model1, tolerance = 0.05)
performance::check_overdispersion(fm_cop_bl_zi_nb_model1)
confint(fm_cop_bl_zi_nb_model1, level = 0.95, method = "profile")
#Ok, final model

anova(fm_cop_bl_nb_model1, fm_cop_bl_zi_nb_model1)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = fm_cop_bl_zi_nb_model1)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)

plot_model(fm_vis_bl_zinb_model2, type = "pred", terms = "Date2")
plot_model(fm_vis_bl_zinb_model2, type = "pred", terms = "Fm_ID")
plot_model(fm_vis_bl_zinb_model2, type = "pred", terms = "Time")


```


### II. Between Resident differences with a Satellite on the lek 

# Testing male behaviour and female choice behaviour between residents in sessions with the satellite



```{r data set prep}

# Data set prep: Only Resident behaviour data set

Session_behav_all_res <- read.csv("Resident cooperation MS Kupan Data/Session_behav_no_state_aggression.csv")

Session_behav_sat <- Session_behav_all_res %>% filter(Condition == "Satellite") 

```


## II/1. Display behaviour

# II/1a. Display activity score


```{r Display activity}

## Models


# Note: Group ID does not explain anything of the variance

# Gaussian
display_sat_lm_mm <- glmmTMB(Total_nr_display ~ Time + Date2 + Fm_ID + (1|Colour_code), data = Session_behav_sat)
summary(display_sat_lm_mm)


# Neg bin
display_sat_nb_mm <- glmmTMB(Total_nr_display ~ Time + Date2 + Fm_ID + (1|Colour_code), data = Session_behav_sat, family = nbinom2)
summary(display_sat_nb_mm)
check_zeroinflation(display_sat_nb_mm, tolerance = 0.05)
check_overdispersion(display_sat_nb_mm)
check_singularity(display_sat_nb_mm)
# zero inflated


# Poisson
display_sat_poi_mm <- glmmTMB(Total_nr_display ~ Time + Date2 + Fm_ID + (1|Colour_code), data = Session_behav_sat, family = poisson(link = "log"))
summary(display_sat_poi_mm)
check_zeroinflation(display_sat_poi_mm, tolerance = 0.05)
check_overdispersion(display_sat_poi_mm)
check_singularity(display_sat_poi_mm)
# zero-inflated, over dispersed


# Zi neg bin
display_sat_zi_nb_m <- glmmTMB(Total_nr_display ~ Time + Date2 + Fm_ID + (1|Colour_code), data = Session_behav_sat, family = nbinom2, zi = ~ 1  + Date2 + Fm_ID + Time)
summary(display_sat_zi_nb_m)
check_zeroinflation(display_sat_zi_nb_m, tolerance = 0.05)
check_overdispersion(display_sat_zi_nb_m)
check_singularity(display_sat_zi_nb_m)
# OK 


# Zi Poisson
display_sat_zi_poi_m <- glmmTMB(Total_nr_display ~ Time + Date2 + Fm_ID + (1|Colour_code), data = Session_behav_sat, family = poisson(link = "log"), zi = ~ 1  + Date2 + Fm_ID + Time)
summary(display_sat_zi_poi_m)
check_zeroinflation(display_sat_zi_poi_m, tolerance = 0.05)
check_overdispersion(display_sat_zi_poi_m)
check_singularity(display_sat_zi_poi_m)
confint(display_sat_zi_poi_m, level = 0.95, method = "profile")
# Ok - final model

anova(display_sat_zi_nb_m, display_sat_zi_poi_m)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = display_sat_zi_poi_m)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)


```


## II/1b. Co-display duration


```{r Co-display duration}


## Date distribution tests on raw data

hist(Session_behav_sat$Co.display_total_duration_s_session)

Session_behav_sat2 <- Session_behav_sat %>% filter(Co.display_total_duration_s_session != 0)

hist(Session_behav_sat2$Co.display_total_duration_s_session)


library(fitdistrplus)
descdist(Session_behav_sat2$Co.display_total_duration_s_session, boot = 1000)

normal_dist <- fitdist((Session_behav_sat2$Co.display_total_duration_s_session), "norm")
plot(normal_dist)

lognormal_dist <- fitdist((Session_behav_sat2$Co.display_total_duration_s_session), "lnorm")
plot(lognormal_dist)

weibull_dist <- fitdist((Session_behav_sat2$Co.display_total_duration_s_session), "weibull")
plot(weibull_dist)

gamma_dist <- fitdist((Session_behav_sat2$Co.display_total_duration_s_session), "gamma")
plot(gamma_dist)
# Failed

plot.legend <- c("normal", "lognormal", "weibull")
denscomp(list(normal_dist,lognormal_dist,weibull_dist), legendtext = plot.legend)
qqcomp(list(normal_dist,lognormal_dist,weibull_dist), legendtext = plot.legend)
cdfcomp(list(normal_dist,lognormal_dist,weibull_dist), legendtext = plot.legend)
ppcomp(list(normal_dist,lognormal_dist,weibull_dist), legendtext = plot.legend)

gofstat(list(normal_dist,lognormal_dist,weibull_dist), fitnames = c("normal", "lognormal", "weibull", "gamma_dist"))

plotdist(log(Session_behav_sat2$Co.display_total_duration_s_session), histo = TRUE, demp = TRUE)



# Log-transformed data

descdist(log(Session_behav_sat2$Co.display_total_duration_s_session), boot = 1000)

normal_dist <- fitdist(log(Session_behav_sat2$Co.display_total_duration_s_session), "norm")
plot(normal_dist)

lognormal_dist <- fitdist(log(Session_behav_sat2$Co.display_total_duration_s_session), "lnorm")
plot(lognormal_dist)

weibull_dist <- fitdist(log(Session_behav_sat2$Co.display_total_duration_s_session), "weibull")
plot(weibull_dist)

gamma_dist <- fitdist(log(Session_behav_sat2$Co.display_total_duration_s_session), "gamma")
plot(gamma_dist)

plot.legend <- c("normal", "lognormal", "weibull", "gamma_dist")
denscomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
qqcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
cdfcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
ppcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)

gofstat(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), fitnames = c("normal", "lognormal", "weibull", "gamma_dist"))

plotdist(log(Session_behav_sat2$Co.display_total_duration_s_session), histo = TRUE, demp = TRUE)

# Log-transformed looks better

hist(log(Session_behav_sat2$Co.display_total_duration_s_session))


## Models

# Transformed variable

Session_behav_sat$Co.display_total_duration_s_session_tr <- ifelse(Session_behav_sat$Co.display_total_duration_s_session == 0, 0, log(Session_behav_sat$Co.display_total_duration_s_session))

# Gaussian
co_display_lm_mm <- glmmTMB(Co.display_total_duration_s_session_tr ~ Total_nr_display  + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, family = gaussian)
summary(co_display_lm_mm)


# gamma hurdle
co_display_gamma_hurdle_mm <- glmmTMB(Co.display_total_duration_s_session_tr ~ Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code), data = Session_behav_sat, family = ziGamma(link="log"), ziformula = ~ 1+ Total_nr_display)
summary(co_display_gamma_hurdle_mm)
check_overdispersion(co_display_gamma_hurdle_mm)
# OK

# lognorm hurdle
co_display_lognorm_hurdle_mm <- glmmTMB(Co.display_total_duration_s_session_tr ~ Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code), data = Session_behav_sat, family = glmmTMB::lognormal(link="log"), ziformula = ~ 1+ Total_nr_display)
summary(co_display_lognorm_hurdle_mm)
check_overdispersion(co_display_lognorm_hurdle_mm)
confint(co_display_lognorm_hurdle_mm, level = 0.95, method = "profile")
# Ok - final model, group ID has no effect

anova(co_display_gamma_hurdle_mm, co_display_lognorm_hurdle_mm)



### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = co_display_lognorm_hurdle_mm)

# Plot residuals
plot(sim_res)
# upper quartile is not fitting well

testDispersion(sim_res)


```



## II/2. Aggressive behaviours

# II/2a. Number of chases against Residents


```{r Chases against residents}

## Models

# Gaussian
chasings_res_lm_mm <- glmmTMB(Chasings_res ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat)
summary(chasings_res_lm_mm)

# Poisson
chasings_res_poi_mm <- glmmTMB(Chasings_res ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, family = poisson(link = "log"))
summary(chasings_res_poi_mm)
performance::check_zeroinflation(chasings_res_poi_mm, tolerance = 0.05)
performance::check_overdispersion(chasings_res_poi_mm)
# over dispersed zero inflated

# Neg bin
chasings_res_nb_mm <- glmmTMB(Chasings_res ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID  + Time +(1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, family = nbinom2)
summary(chasings_res_nb_mm)
performance::check_zeroinflation(chasings_res_nb_mm, tolerance = 0.05)
performance::check_overdispersion(chasings_res_nb_mm)
# Zero- inflated

# Poisson zi
chasings_res_zi_poi_mm <- glmmTMB(Chasings_res ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time +(1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, family = poisson(link = "log"), zi = ~ 1 +  Total_nr_display)
summary(chasings_res_zi_poi_mm)
performance::check_zeroinflation(chasings_res_zi_poi_mm, tolerance = 0.05)
performance::check_overdispersion(chasings_res_zi_poi_mm)
confint(chasings_res_zi_poi_mm)
# Ok - final model

# chases res nbinom zi
chasings_res_zi_nb_mm <- glmmTMB(Chasings_res ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) +(1|Colour_code), data = Session_behav_sat, family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(chasings_res_zi_nb_mm)
performance::check_zeroinflation(chasings_res_zi_nb_mm, tolerance = 0.05)
performance::check_overdispersion(chasings_res_zi_nb_mm)
# Zero inflated


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = chasings_res_zi_poi_mm)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok

```



# II/2b. Number of attacks against Residents



```{r Attacks against Residents}

## Models

# Gaussian
attacks_res_lm_mm <- glmmTMB(Aggression_res_attack_approach ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat)
summary(attacks_res_lm_mm)


# Neg bin
attacks_res_nb_mm <- glmmTMB(Aggression_res_attack_approach ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = nbinom2)
summary(attacks_res_nb_mm)
performance::check_zeroinflation(attacks_res_nb_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_res_nb_mm)
confint(attacks_res_nb_mm, level = 0.95, method = "profile")
# Ok - final model


# Poisson
attacks_res_poi_mm <- glmmTMB(Aggression_res_attack_approach ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = poisson(link = "log"))
summary(attacks_res_poi_mm)
performance::check_zeroinflation(attacks_res_poi_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_res_poi_mm)
# Zi + od


# Zi neg bin
attacks_res_nb_zi_mm <- glmmTMB(Aggression_res_attack_approach ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = nbinom2, zi = ~ 1 +  Total_nr_display)
summary(attacks_res_nb_zi_mm)
performance::check_zeroinflation(attacks_res_nb_zi_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_res_nb_zi_mm)
# Ok

anova(attacks_res_nb_mm, attacks_res_nb_zi_mm)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = attacks_res_nb_mm)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok

```


## II/2c. Duration of fights


```{r Fight durations}

## Date distribution tests on raw data

hist(Session_behav_sat$Fight_dur_s)

Session_behav_sat2 <- Session_behav_sat %>% filter(Fight_dur_s != 0)

hist(Session_behav_sat2$Fight_dur_s)


library(fitdistrplus)
descdist(Session_behav_sat2$Fight_dur_s, boot = 1000)
# Yuck

# Log-transformed data
descdist(log(Session_behav_sat2$Fight_dur_s), boot = 1000)
# Looks good

normal_dist <- fitdist(Session_behav_sat2$Fight_dur_s, "norm")
plot(normal_dist)

lognormal_dist <- fitdist(Session_behav_sat2$Fight_dur_s, "lnorm")
plot(lognormal_dist)

weibull_dist <- fitdist(Session_behav_sat2$Fight_dur_s, "weibull")
plot(weibull_dist)

gamma_dist <- fitdist(Session_behav_sat2$Fight_dur_s, "gamma")
plot(gamma_dist)

plot.legend <- c("normal", "lognormal", "weibull", "gamma_dist")
denscomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
qqcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
cdfcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
ppcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)

gofstat(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), fitnames = c("normal", "lognormal", "weibull", "gamma_dist"))

plotdist(log(Session_behav_sat2$Fight_dur_s), histo = TRUE, demp = TRUE)

# Lognorm loooks the best


## Models

# Gaussian
figth_dur_mm_lm <- glmmTMB(Fight_dur_s ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Session_ID), data = Session_behav_sat, family = gaussian, ziformula = ~ 1 +  Total_nr_display)
summary(figth_dur_mm_lm)


# Gamma hurdle
figth_dur_mm_gamma <- glmmTMB(Fight_dur_s ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Session_ID), data = Session_behav_sat, family = ziGamma(link="log"), ziformula = ~ 1 +  Total_nr_display)
summary(figth_dur_mm_gamma)
performance::check_overdispersion(figth_dur_mm_gamma)
performance::confint(figth_dur_mm_gamma, level = 0.95, method = "profile")
# Ok - Colour_code has very little effect, session ID is used instead  - Final model


# Lognorm hurdle
figth_dur_mm_lnorm <- glmmTMB(Fight_dur_s ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time +(1|Session_ID), data = Session_behav_sat,family = glmmTMB::lognormal(link="log"),  ziformula = ~  Total_nr_display)
summary(figth_dur_mm_lnorm)
performance::check_overdispersion(figth_dur_mm_lnorm)
# Ok - Colour_code has very little effect

anova(figth_dur_mm_lm, figth_dur_mm_gamma, figth_dur_mm_lnorm)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = figth_dur_mm_gamma)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok


```


## II/2d. Number of chases against Satellite

```{r Satellite chases}

## Models

# Gaussial
chasigs_sat_lm_mm <- glmmTMB(Chasings_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat)
summary(chasigs_sat_lm_mm)


# Neg bin
chasigs_sat_nb_mm <- glmmTMB(Chasings_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = nbinom2)
summary(chasigs_sat_nb_mm)
performance::check_zeroinflation(chasigs_sat_nb_mm, tolerance = 0.05)
performance::check_overdispersion(chasigs_sat_nb_mm)
confint(chasigs_sat_nb_mm, level = 0.95, method = "profile")
# Ok - best fit final model


# Poisson
chasigs_sat_poi_mm <- glmmTMB(Chasings_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = poisson(link = "log"))
summary(chasigs_sat_poi_mm)
performance::check_zeroinflation(chasigs_sat_poi_mm, tolerance = 0.05)
performance::check_overdispersion(chasigs_sat_poi_mm)
# Zi


# Zi neg bin
chasigs_sat_zi_nb_mm <- glmmTMB(Chasings_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time +(1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = nbinom2, zi = ~ 1 )
summary(chasigs_sat_zi_nb_mm)
performance::check_zeroinflation(chasigs_sat_zi_nb_mm, tolerance = 0.05)
performance::check_overdispersion(chasigs_sat_zi_nb_mm)
# Ok, Total_nr_display is not converging in the zero inflated part 


# Zi Poisson
chasigs_sat_zi_poi_mm <- glmmTMB(Chasings_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time +(1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, family = poisson(link = "log"), zi = ~ 1 +  Total_nr_display)
summary(chasigs_sat_zi_poi_mm)
performance::check_zeroinflation(chasigs_sat_zi_poi_mm, tolerance = 0.05)
performance::check_overdispersion(chasigs_sat_zi_poi_mm)
# Ok 

anova(chasigs_sat_nb_mm, chasigs_sat_zi_nb_mm, chasigs_sat_zi_poi_mm)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = chasigs_sat_nb_mm)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok


```


## II/2e. Number of attacks against Satellite


```{r Satellite attacks}

## Models

# Gaussian
attacks_sat_lm_mm <- glmmTMB(Attacks_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code) + (1|Combo_lek) , data = Session_behav_sat)
summary(attacks_sat_lm_mm)


# Neg bin
attacks_sat_nb_mm <- glmmTMB(Attacks_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code) + (1|Combo_lek) , data = Session_behav_sat, family = nbinom2)
summary(attacks_sat_nb_mm)
performance::check_zeroinflation(attacks_sat_nb_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_sat_nb_mm)
# Ok


# Poisson
attacks_sat_poi_mm <- glmmTMB(Attacks_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time + (1|Colour_code) + (1|Combo_lek) , data = Session_behav_sat, family = poisson(link = "log"))
summary(attacks_sat_poi_mm)
performance::check_zeroinflation(attacks_sat_poi_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_sat_poi_mm)
confint(attacks_sat_poi_mm, level = 0.95, method = "profile")
# Ok - Final model!


# Zi neg bin
attacks_sat_zi_nb_mm <- glmmTMB(Attacks_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID +  Time + (1|Colour_code) + (1|Combo_lek) , data = Session_behav_sat, family = nbinom2, zi = ~ 1)
summary(attacks_sat_zi_nb_mm)
performance::check_zeroinflation(attacks_sat_zi_nb_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_sat_zi_nb_mm)
# Ok


# Zi Poisson
attacks_sat_zi_poi_mm <- glmmTMB(Attacks_sat ~  scale(Co.display_total_duration_s_session) +  Total_nr_display  + Date2 + Fm_ID + Time +  (1|Colour_code) + (1|Combo_lek) , data = Session_behav_sat, family = poisson(link = "log"), zi = ~ 1 +  Total_nr_display)
summary(attacks_sat_zi_poi_mm)
performance::check_zeroinflation(attacks_sat_zi_poi_mm, tolerance = 0.05)
performance::check_overdispersion(attacks_sat_zi_poi_mm)
# Ok

anova(attacks_sat_nb_mm, attacks_sat_poi_mm, attacks_sat_zi_nb_mm, attacks_sat_zi_poi_mm)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = attacks_sat_poi_mm)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok


```


## II/3. Social predictors of female mate choice

# II/3a. Total number of female visits


```{r Female visit numbers}

## Date distribution tests

hist(Session_behav_sat$Total_visit_nr_all_females)

sum(Session_behav_sat$Total_visit_nr_all_females) # 408

# Visits by female compartments

sum(Session_behav_sat$Total_visit_nr_all_females[Session_behav_sat$Fm_ID == "Fm1"]) # 81

sum(Session_behav_sat$Total_visit_nr_all_females[Session_behav_sat$Fm_ID == "Fm2"]) # 327


## Model

# Gaussian - preliminary analysis
res_session_vis_nr_lm <- glmmTMB(Total_visit_nr_all_females ~  scale(Co.display_total_duration_s_session)  +  Total_nr_display + Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat, zi = ~ 0)
summary(res_session_vis_nr_lm)


# Neg bin
res_session_vis_nr_nb <- glmmTMB(Total_visit_nr_all_females ~ Total_nr_display +  scale(Co.display_total_duration_s_session) +  Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat,  family = nbinom2)
summary(res_session_vis_nr_nb)
performance::check_zeroinflation(res_session_vis_nr_nb, tolerance = 0.05)
performance::check_overdispersion(res_session_vis_nr_nb)
performance::check_singularity(res_session_vis_nr_nb, tol = 1e-05)
confint(res_session_vis_nr_nb, level = 0.95, method = "profile")
# Ok -best fit


# Neg bin zero inflated
res_session_vis_nr_zero_infl <- glmmTMB(Total_visit_nr_all_females ~ scale(Co.display_total_duration_s_session) + Total_nr_display + Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat,  family = nbinom2, zi = ~ 1)
summary(res_session_vis_nr_zero_infl)
performance::check_zeroinflation(res_session_vis_nr_zero_infl, tolerance = 0.05)
performance::check_overdispersion(res_session_vis_nr_zero_infl)
performance::check_singularity(res_session_vis_nr_zero_infl, tol = 1e-05)
# Ok 


# Neg bin zero inflated2
res_session_vis_nr_zero_infl2 <- glmmTMB(Total_visit_nr_all_females ~ scale(Co.display_total_duration_s_session) + Total_nr_display + Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(res_session_vis_nr_zero_infl2)
performance::check_zeroinflation(res_session_vis_nr_zero_infl2, tolerance = 0.05)
performance::check_overdispersion(res_session_vis_nr_zero_infl2)
performance::check_singularity(res_session_vis_nr_zero_infl2, tol = 1e-05)
# OK, best model fit


# Poisson
res_session_vis_nr_poi <- glmmTMB(Total_visit_nr_all_females ~ scale(Co.display_total_duration_s_session)  +  Total_nr_display + Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat,  family = poisson(log), zi = ~ 0)
summary(res_session_vis_nr_poi)
performance::check_zeroinflation(res_session_vis_nr_poi, tolerance = 0.05)
performance::check_overdispersion(res_session_vis_nr_poi)
performance::check_singularity(res_session_vis_nr_poi, tol = 1e-05)
# Zi, over dispersed


# Poisson zero inflated
res_session_vis_poi_zero_infl <- glmmTMB(Total_visit_nr_all_females ~ scale(Co.display_total_duration_s_session) + Total_nr_display + Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat,  family = poisson(log), zi = ~ 1)
summary(res_session_vis_poi_zero_infl)
performance::check_zeroinflation(res_session_vis_poi_zero_infl, tolerance = 0.05)
performance::check_overdispersion(res_session_vis_poi_zero_infl)
performance::check_singularity(res_session_vis_poi_zero_infl, tol = 1e-05)
# Zero-inflated


# Poisson zero inflated2
res_session_vis_poi_zero_infl2 <- glmmTMB(Total_visit_nr_all_females ~ scale(Co.display_total_duration_s_session) + Total_nr_display + Fm_ID + Date2 + (1|Combo_lek) + (1|Colour_code), data = Session_behav_sat,  family = poisson(log), zi = ~ 1 + Total_nr_display)
summary(res_session_vis_poi_zero_infl2)
performance::check_zeroinflation(res_session_vis_poi_zero_infl2, tolerance = 0.05)
performance::check_overdispersion(res_session_vis_poi_zero_infl2)
performance::check_singularity(res_session_vis_poi_zero_infl2, tol = 1e-05)
# Zero-inflated over dispersed


anova(res_session_vis_nr_nb, res_session_vis_nr_zero_infl, res_session_vis_nr_zero_infl2)

model.set <- list(res_session_vis_nr_nb, res_session_vis_nr_zero_infl, res_session_vis_nr_zero_infl2)
names <- c(  "mm_nb", "mm_zi_nbb","mm_zi_nbb2")
aictab(model.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = res_session_vis_nr_nb)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)


```


# II/3b. Total duration of female visits


```{r Duration of female visits}

## Date distribution tests on raw data

hist(Session_behav_sat$Total_visit_duration_all_females)

Session_behav_sat2 <- Session_behav_sat %>% filter(Total_visit_duration_all_females != 0)

hist(Session_behav_sat2$Total_visit_duration_all_females)

Session_behav_sat2$Total_visit_duration_all_females_sc <- as.numeric(scale(Session_behav_sat2$Total_visit_duration_all_females))

hist(Session_behav_sat2$Total_visit_duration_all_females_sc)

library(fitdistrplus)
descdist(Session_behav_sat2$Total_visit_duration_all_females, boot = 1000)

# Log-transformed data

descdist(log(Session_behav_sat2$Total_visit_duration_all_females), boot = 1000)

normal_dist <- fitdist(log(Session_behav_sat2$Total_visit_duration_all_females), "norm")
plot(normal_dist)

lognormal_dist <- fitdist(log(Session_behav_sat2$Total_visit_duration_all_females), "lnorm")
plot(lognormal_dist)

weibull_dist <- fitdist(log(Session_behav_sat2$Total_visit_duration_all_females), "weibull")
plot(weibull_dist)

gamma_dist <- fitdist(log(Session_behav_sat2$Total_visit_duration_all_females), "gamma")
plot(gamma_dist)

plot.legend <- c("normal", "lognormal", "weibull", "gamma_dist")
denscomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
qqcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
cdfcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
ppcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)

gofstat(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), fitnames = c("normal", "lognormal", "weibull", "gamma_dist"))

plotdist(log(Session_behav_sat2$Total_visit_duration_all_females), histo = TRUE, demp = TRUE)



## Models

# Transformed variable
Session_behav_sat$Total_visit_duration_all_females_tr <- ifelse(Session_behav_sat$Total_visit_duration_all_females == 0, 0, log(Session_behav_sat$Total_visit_duration_all_females))


# Fitting hurdle ln, gamma model and lognorm model - lognorm is better!
# Random variables have no effect


# Gaussian model
visit_dur_lm_m <- glmmTMB(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + scale(Co.display_total_duration_s_session)  +  Total_nr_display + (1|Session_ID), data=Session_behav_sat)
summary(visit_dur_lm_m)
# Ok


# Gaussian model zi
visit_dur_lm_zi_m <- glmmTMB(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + scale(Co.display_total_duration_s_session)  +  Total_nr_display + (1|Session_ID), data=Session_behav_sat,family = gaussian(), ziformula = ~ 1)
summary(visit_dur_lm_zi_m)
# Not converging with Total_nr_display in the zi part


# Gamma models
visit_dur_gamma_hurdle_m <- glmmTMB(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + scale(Co.display_total_duration_s_session)  +  Total_nr_display + (1|Session_ID), data=Session_behav_sat, family = ziGamma(link="log"), ziformula = ~ 1 +  Total_nr_display)
summary(visit_dur_gamma_hurdle_m)
#Ok


# Log-norm models
visit_dur_lognorm_hurdle_m <- glmmTMB(Total_visit_duration_all_females_tr ~ Date2 + Fm_ID + scale(Co.display_total_duration_s_session)  +  Total_nr_display + (1|Session_ID), data=Session_behav_sat, family = glmmTMB::lognormal(link="log"), ziformula = ~ 1  +  Total_nr_display)
summary(visit_dur_lognorm_hurdle_m)
confint(visit_dur_lognorm_hurdle_m, level = 0.95, method = "profile")
# Ok, best model fit, Colour code and group Id no effect

anova(visit_dur_lm_m, visit_dur_lm_zi_m, visit_dur_gamma_hurdle_m, visit_dur_lognorm_hurdle_m)


# AIC model selection
cand.set <- list(visit_dur_lm_m, visit_dur_gamma_hurdle_m, visit_dur_lognorm_hurdle_m)
names <- c("lm","gamma", "lognorm")
aictab(cand.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)


### Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = visit_dur_lognorm_hurdle_m)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok



```


# II/3c. Number of copulation attempts


```{r Copulation number models}

## Date distribution tests on raw data

hist(Session_behav_sat$Copulation_nr)

sum(Session_behav_sat$Copulation_nr) # 84

# Copulations by female compartments

sum(Session_behav_sat$Copulation_nr[Session_behav_sat$Fm_ID == "Fm1"]) # 48

sum(Session_behav_sat$Copulation_nr[Session_behav_sat$Fm_ID == "Fm2"]) # 36

## Copulation and co-display relationships

# Copulating but non co-displaying males across sessions
Cop_no_codisp <- Session_behav_sat %>% filter(Copulation_nr > 0 & Co_displ_occurrence == 0)  ## 2 


## Models: non zero-inflated models

# Copulation_nr refers to Copulation attempts which include interrupted and successful copulations, thus reflects female interest that success (Copulation_nr == Total_copulation_nr)

# Date: Co-display duration and Date have a strong relationship therefore Date is removed from the models - adding Date does not improve the model fit, models with Date always under perform the ones without

# Random structure: Session_ID does not add to varianve - I use Colour_code (which is Male ID)


# Gaussian
cop_nr_lm_mm <- glmmTMB(Copulation_nr ~ Fm_ID + Date2 + scale(Co.display_total_duration_s_session) +  Total_nr_display  + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat)
summary(cop_nr_lm_mm)
# Co-display has an effect but singularity

# Neg bin
cop_nr_nb_mm <- glmmTMB(Copulation_nr ~  scale(Co.display_total_duration_s_session) +  Total_nr_display + Date2 + Fm_ID  + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, 
                      family = nbinom2, zi = ~ 0)
summary(cop_nr_nb_mm)
performance::check_zeroinflation(cop_nr_nb_mm, tolerance = 0.05)
performance::check_overdispersion(cop_nr_nb_mm)
confint(cop_nr_nb_mm, level = 0.95, method = "profile")
confint(cop_nr_nb_mm, level = 0.95)
# Ok - best model fit

# Poisson
cop_nr_poisson_mm <- glmmTMB(Copulation_nr ~ scale(Co.display_total_duration_s_session) +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, family = poisson(link = "log"))
summary(cop_nr_poisson_mm)
performance::check_zeroinflation(cop_nr_poisson_mm, tolerance = 0.05)
performance::check_overdispersion(cop_nr_poisson_mm)
# Zero-inflated


# Zi neg bin
cop_nr_nb_zi_mm <- glmmTMB(Copulation_nr ~  scale(Co.display_total_duration_s_session) +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, 
                      family = nbinom2, zi = ~ 1)
summary(cop_nr_nb_zi_mm)
performance::check_zeroinflation(cop_nr_nb_zi_mm, tolerance = 0.05)
performance::check_overdispersion(cop_nr_nb_zi_mm)
# Ok - convergence issue with Total_nr_display in the zi part


# Zi poisson
cop_nr_poi_zi_mm <- glmmTMB(Copulation_nr ~  scale(Co.display_total_duration_s_session) +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, 
                      family = poisson(link = "log"), zi = ~ 1 + Total_nr_display)
summary(cop_nr_poi_zi_mm)
performance::check_zeroinflation(cop_nr_poi_zi_mm, tolerance = 0.05)
performance::check_overdispersion(cop_nr_poi_zi_mm)
# Ok

anova(cop_nr_nb_mm, cop_nr_nb_zi_mm, cop_nr_poi_zi_mm )

model.set <- list( cop_nr_nb_mm, cop_nr_nb_zi_mm, cop_nr_poi_zi_mm )
names <- c("mm_nb",  "mm_zi_nb", "mm_poi_zi")
aictab(model.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = cop_nr_nb_mm)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok

```


# II/3d. Number of successful copulations


```{r Successful copulations}


## Date distribution tests on raw data

hist(Session_behav_sat$Total_successful_copulations)

sum(Session_behav_sat$Total_successful_copulations) # 57

# Copulations by female compartments

sum(Session_behav_sat$Total_successful_copulations[Session_behav_sat$Fm_ID == "Fm1"]) # 31

sum(Session_behav_sat$Total_successful_copulations[Session_behav_sat$Fm_ID == "Fm2"]) # 26


## Models

# Gaussian
res_session_suc_cop_nr_lm <- glmmTMB(Total_successful_copulations ~ scale(Co.display_total_duration_s_session)  +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat, zi = ~ 0)
summary(res_session_suc_cop_nr_lm)


# Neg bin
res_session_suc_cop_nr_nb <- glmmTMB(Total_successful_copulations ~ scale(Co.display_total_duration_s_session)  +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat,  family = nbinom2, zi = ~ 0)
summary(res_session_suc_cop_nr_nb)
performance::check_zeroinflation(res_session_suc_cop_nr_nb, tolerance = 0.05)
performance::check_overdispersion(res_session_suc_cop_nr_nb)
performance::check_singularity(res_session_suc_cop_nr_nb, tol = 1e-05)
# Ok 


# Poisson
res_session_suc_cop_nr_poi <- glmmTMB(Total_successful_copulations ~ scale(Co.display_total_duration_s_session)  +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat,  family = poisson(log), zi = ~ 0)
summary(res_session_suc_cop_nr_poi)
performance::check_zeroinflation(res_session_suc_cop_nr_poi, tolerance = 0.05)
performance::check_overdispersion(res_session_suc_cop_nr_poi)
performance::check_singularity(res_session_suc_cop_nr_poi, tol = 1e-05)
# Ok


# zi neg bin
res_session_suc_cop_nr_nb_zi <- glmmTMB(Total_successful_copulations ~ scale(Co.display_total_duration_s_session)  +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat,  family = nbinom2, zi = ~ Total_nr_display)
summary(res_session_suc_cop_nr_nb_zi)
performance::check_zeroinflation(res_session_suc_cop_nr_nb_zi, tolerance = 0.05)
performance::check_overdispersion(res_session_suc_cop_nr_nb_zi)
performance::check_singularity(res_session_suc_cop_nr_nb_zi, tol = 1e-05)
confint(res_session_suc_cop_nr_nb_zi, level = 0.95, method = "profile")
# Ok - best model

# zi poi
res_session_suc_cop_nr_poi_zi <- glmmTMB(Total_successful_copulations ~ scale(Co.display_total_duration_s_session)  +  Total_nr_display + Date2 + Fm_ID + (1|Colour_code) + (1|Combo_lek), data = Session_behav_sat,  family = poisson(log), zi = ~ Total_nr_display)
summary(res_session_suc_cop_nr_poi_zi)
performance::check_zeroinflation(res_session_suc_cop_nr_poi_zi, tolerance = 0.05)
performance::check_overdispersion(res_session_suc_cop_nr_poi_zi)
performance::check_singularity(res_session_suc_cop_nr_poi_zi, tol = 1e-05)
# Ok


anova(res_session_suc_cop_nr_nb, res_session_suc_cop_nr_poi, res_session_suc_cop_nr_nb_zi, res_session_suc_cop_nr_poi_zi)

model.set <- list( res_session_suc_cop_nr_lm, res_session_suc_cop_nr_nb, res_session_suc_cop_nr_poi, res_session_suc_cop_nr_nb_zi)
names <- c("mm_lm","mm_nb", "mm_poi", "mm_zi_nb")
aictab(model.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = res_session_suc_cop_nr_nb_zi)

# Plot residuals
plot(sim_res)
# OK

testDispersion(sim_res)
# Ok


```



### III. Within-Resident differences between Satellite and Control conditions


```{r Data set prep}

# Only Resident behaviour data set
Session_behav_all_res <- read.csv("Resident cooperation MS Kupan Data/Session_behav_no_state_aggression.csv")

## Week refers to the time period a group of residents spent together (= Group period) and it is 6 consecutive days  

# Slpitting Week7 a + m to week7 and week8 to have the same structure as before

Combo_behav_no_state <- NULL

Combo_behav_no_state <- Session_behav_all_res

Combo_behav_no_state$Week <- ifelse(Combo_behav_no_state$Date == 530 | Combo_behav_no_state$Date == 602 | Combo_behav_no_state$Date == 531 & Combo_behav_no_state$Time == "m"| Combo_behav_no_state$Date == 603 & Combo_behav_no_state$Time == "m", 7, Combo_behav_no_state$Week)

Combo_behav_no_state$Week <- ifelse(Combo_behav_no_state$Week == "7a"|Combo_behav_no_state$Week == "7m", 8, Combo_behav_no_state$Week)

Combo_behav_no_state$Combo_lek_week <- paste(Combo_behav_no_state$Combo_lek, Combo_behav_no_state$Week, sep = "_")

# Creating combo/day ID within conditions

Combo_behav_no_state <- Combo_behav_no_state %>% group_by(Combo_lek_week, Condition) %>% mutate(Combo_day = match(paste(Date2,Time), unique(paste(Date2, Time)))) %>% arrange(Session_ID) %>% relocate(Combo_day, .after = Combo_lek)

Combo_behav_no_state <- Combo_behav_no_state %>% group_by(Combo_lek) %>% arrange(Week) %>% mutate(Combo_lek_repeat = as.numeric(as.factor(Week))) %>% relocate(Combo_lek_repeat, .after = Combo_day)

Combo_behav_no_state <- Combo_behav_no_state %>% mutate(Co_disp_score = round(Co.display_total_duration_s_session / 600, digits = 0)) %>% relocate(Co_disp_score, .after = Co_disp_ord ) %>% 
  group_by(Combo_lek_week, Colour_code) %>% mutate(Co_disp_score_week = sum(Co_disp_score)) %>% relocate(Co_disp_score_week, .after = Co_disp_score )

colnames(Combo_behav_no_state)

Group_period_sum <- Combo_behav_no_state %>% group_by(Colour_code, Condition, Week, Fm_ID, Combo_lek_week, Combo_lek) %>% 
  summarise(across(c(Session_nr, Female_max_id,Total_visit_duration_all_females,Total_visit_nr_all_females,Visits_longest_s,Visit_occurrence, Total_nr_display, Co_disp_score, Interrupted_copulations_nr_OtherR,Interrupted_copulations_nr_OtherS,Interrupted_copulations_nr_PartnerR,Interrupted_copulations_nr_PartnerS, Successful_copulations_nr,Interrupted_total,Mount_nr,Crouching_nr, Copulation_attempt, Copulation_nr, Total_successful_copulations, Co.display_total_nr_session, Co.display_total_duration_s_session,Single_display_total_duration_s_session, Single_display_to_satellite_total_nr_session, Single_display_to_both_total_nr_session, Single_display_to_both_total_duration_s_session, Paired_state_total_nr_session, Paired_state_total_duration_s_session, Co_displ_occurrence, Copulation_occurrence_successful,Copulation_occurrence, Co_disp_session, Single_display_total_duration_s_session, Single_display_to_satellite_total_nr_session, Single_display_to_both_total_nr_session, Single_display_to_both_total_duration_s_session, Copulation_occurrence_successful, Copulation_occurrence, Single_display_duration_mean_s_session, Single_display_duration_std_dev_session,Visits_longest_s, Chasings_total, Chasings_res, Chasings_sat, Chasings_marg, Attacks_total, Attacks_res, Attacks_sat, Attacks_marg, Approaches, Fight_dur_s, Aggression_res_total,  Aggression_sat_total, Aggression_total, Aggression_res_attack_approach,  Aggression_attack_approach_total), sum, na.rm = TRUE))

# Creating a co-display variable for co-diplaying individuals in a session for both conditions 
Group_period_sum <- Group_period_sum %>% group_by(Combo_lek_week, Colour_code) %>% mutate(Co.display_total_duration_s_session2 = sum(Co.display_total_duration_s_session)) %>% relocate(Co.display_total_duration_s_session2, .after = Co.display_total_duration_s_session)

Group_period_sum <- Group_period_sum %>% group_by(Combo_lek) %>% arrange(Week) %>% mutate(Combo_lek_repeat = as.numeric(as.factor(Week)))

# Combo_rank by display
Group_period_sum <- Group_period_sum %>% group_by(Combo_lek_week, Condition) %>% arrange(desc(Total_nr_display)) %>% mutate(Combo_display_rank = row_number(desc(Total_nr_display))) %>% relocate(Combo_display_rank, .after = Total_nr_display)

# Combo_co_disp_rank
Group_period_sum <- Group_period_sum %>% group_by(Combo_lek_week, Condition) %>% arrange(desc(Co.display_total_duration_s_session2)) %>% mutate(Combo_co_disp_rank = row_number(desc(Co.display_total_duration_s_session2))) %>% mutate(Combo_co_disp_rank = if_else(Co.display_total_duration_s_session2 == 0, 3, Combo_co_disp_rank)) %>%
  relocate(Combo_co_disp_rank, .after = Combo_display_rank)

sum(Group_period_sum$Copulation_nr) # 228

write.csv(Group_period_sum, "Resident cooperation MS Kupan Data/Group_period_sums.csv")

```



## III/1. Display


```{r Display activity score}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")


## Model 1: Only intercept models

# Gaussian
combo_displ_nr_lm_mm <- glmmTMB(Total_nr_display ~  Condition +  Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_displ_nr_lm_mm)

# Neg bin models 
combo_displ_nr_nb_mm <- glmmTMB(Total_nr_display ~  Condition +  Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_displ_nr_nb_mm)
performance::check_zeroinflation(combo_displ_nr_nb_mm, tolerance = 0.05)
check_overdispersion(combo_displ_nr_nb_mm)
check_singularity(combo_displ_nr_nb_mm, tol = 1e-05)
# Zero-inflated

# Poisson model
combo_displ_nr_poi_mm <- glmmTMB(Total_nr_display ~  Condition + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,family = poisson(link = log))
summary(combo_displ_nr_poi_mm)
performance::check_zeroinflation(combo_displ_nr_poi_mm, tolerance = 0.05)
check_overdispersion(combo_displ_nr_poi_mm)
# Zero inflated and over dispersed


# Zero inflation neg bin model
combo_displ_nr_zi_nb_mm <- glmmTMB(Total_nr_display ~  Condition + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1)
summary(combo_displ_nr_zi_nb_mm)
performance::check_zeroinflation(combo_displ_nr_zi_nb_mm)
check_overdispersion(combo_displ_nr_zi_nb_mm)
check_singularity(combo_displ_nr_zi_nb_mm)
confint(combo_displ_nr_zi_nb_mm, level = 0.95, method = "profile")
# Ok, final model


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_displ_nr_zi_nb_mm)

# Plot residuals
plot(sim_res)
# Fit is not very good at the upper quartile

testDispersion(sim_res)
# Ok



## Model 2: intercept/slope models (with condition as slope):these are not converging well and are zero inflated or over dispersed so they were not used

# Gaussian 
combo_displ_nr_sl_mm_lm <- glmmTMB(Total_nr_display ~ Condition + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_displ_nr_sl_mm_lm)
# Ok

# Neg bin
combo_displ_nr_sl_mm_nb <- glmmTMB(Total_nr_display ~ Condition + Week  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = nbinom2)
summary(combo_displ_nr_sl_mm_nb)
performance::check_zeroinflation(combo_displ_nr_sl_mm_nb)
check_overdispersion(combo_displ_nr_sl_mm_nb)
# Zero-inflated, underdispersed + slope var is very little

# Poisson model
combo_displ_nr_sl_mm_poi <- glmmTMB(Total_nr_display ~ Condition + Week  +  (Condition|Combo_lek_week:Colour_code), family = poisson(link = log), data = Group_period_sum)
summary(combo_displ_nr_sl_mm_poi)
performance::check_zeroinflation(combo_displ_nr_sl_mm_poi)
check_overdispersion(combo_displ_nr_sl_mm_poi)
# Zero inflated

combo_displ_nr_poi_sl_mm <- glmmTMB(Total_nr_display ~  Condition + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~ 1)
summary(combo_displ_nr_poi_sl_mm)
performance::check_zeroinflation(combo_displ_nr_poi_sl_mm)
check_overdispersion(combo_displ_nr_poi_sl_mm)
check_singularity(combo_displ_nr_poi_sl_mm)
# Slope var is very little, still underdispersed


```


## III/2. Aggression models


## III/2a. Number of chases against Residents


```{r Number of chases against Residents}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")


## Model 1: Only intercept models

# Gaussian
combo_aggression_res_chasing_lm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display, data = Group_period_sum)
summary(combo_aggression_res_chasing_lm)
# Combo_lek_week no effect


# Neg bin
combo_aggression_res_chasing_nb_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_res_chasing_nb_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_nb_mm)
check_overdispersion(combo_aggression_res_chasing_nb_mm)
check_singularity(combo_aggression_res_chasing_nb_mm)
# zero_inflated


# Poisson
combo_aggression_res_chasing_nb_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log))
summary(combo_aggression_res_chasing_nb_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_nb_mm)
check_overdispersion(combo_aggression_res_chasing_nb_mm)
check_singularity(combo_aggression_res_chasing_nb_mm)
# Zero-inflated, over dispersed


# Zi neg bin
combo_aggression_res_chasing_nb_zi_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_res_chasing_nb_zi_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_nb_zi_mm)
check_overdispersion(combo_aggression_res_chasing_nb_zi_mm)
check_singularity(combo_aggression_res_chasing_nb_zi_mm)
confint(combo_aggression_res_chasing_nb_zi_mm, level = 0.95)
# Ok, Final model


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_aggression_res_chasing_nb_zi_mm)

# Plot residuals
plot(sim_res)
# Ok

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope) - with condition slop they don't converge or the slope does not improve the model - these are not used

#Gaussian
combo_aggression_res_chasing_sl_lm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_aggression_res_chasing_sl_lm)

# Neg bin
combo_aggression_res_chasing_sl__nb_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_res_chasing_sl__nb_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_sl__nb_mm)
check_overdispersion(combo_aggression_res_chasing_sl__nb_mm)
check_singularity(combo_aggression_res_chasing_sl__nb_mm)
# zero_inflated, slope does not add to variance

# Poisson
combo_aggression_res_chasing_sl__nb_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log))
summary(combo_aggression_res_chasing_sl__nb_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_sl__nb_mm)
check_overdispersion(combo_aggression_res_chasing_sl__nb_mm)
check_singularity(combo_aggression_res_chasing_sl__nb_mm)
# Zero-inflated

# Zi neg bin
combo_aggression_res_chasing_sl__nb_zi_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_res_chasing_sl__nb_zi_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_sl__nb_zi_mm)
check_overdispersion(combo_aggression_res_chasing_sl__nb_zi_mm)
check_singularity(combo_aggression_res_chasing_sl__nb_zi_mm)
# Ok, with slope not converging well

# Zi poisson
combo_aggression_res_chasing_sl__nb_zi_mm <- glmmTMB(Chasings_res ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~ 1 + Total_nr_display)
summary(combo_aggression_res_chasing_sl__nb_zi_mm)
performance::check_zeroinflation(combo_aggression_res_chasing_sl__nb_zi_mm)
check_overdispersion(combo_aggression_res_chasing_sl__nb_zi_mm)
check_singularity(combo_aggression_res_chasing_sl__nb_zi_mm)
# not converging

```


## III/2b. Number of attacks against Residents


```{r Number of attacks against Residents}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")

## Model 1: Only intercept models

# Gaussian
combo_aggression_res_attack_lm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_aggression_res_attack_lm)

# Neg bin
combo_aggression_res_attack_nb_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_res_attack_nb_mm)
performance::check_zeroinflation(combo_aggression_res_attack_nb_mm)
check_overdispersion(combo_aggression_res_attack_nb_mm)
check_singularity(combo_aggression_res_attack_nb_mm)
confint(combo_aggression_res_attack_nb_mm, level = 0.95, method = "profile")
# Ok - final model

# Poisson
combo_aggression_res_attack_poi_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"))
summary(combo_aggression_res_attack_poi_mm)
performance::check_zeroinflation(combo_aggression_res_attack_poi_mm)
check_overdispersion(combo_aggression_res_attack_poi_mm)
check_singularity(combo_aggression_res_attack_poi_mm)
# Zero inflated, over dispersed

# Zi neg bin
combo_aggression_res_attack_nb_zi_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_res_attack_nb_zi_mm)
performance::check_zeroinflation(combo_aggression_res_attack_nb_zi_mm)
check_overdispersion(combo_aggression_res_attack_nb_zi_mm)
check_singularity(combo_aggression_res_attack_nb_zi_mm)
# Ok but no Total_nr_display effect in the zi part

anova(combo_aggression_res_attack_nb_mm, combo_aggression_res_attack_nb_zi_mm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_aggression_res_attack_nb_mm)

# Plot residuals
plot(sim_res)
# Ok

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope)

# Gaussian
combo_aggression_res_attack_sl_lm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_aggression_res_attack_sl_lm)

# Neg bin
combo_aggression_res_attack_sl_nb_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_res_attack_sl_nb_mm)
performance::check_zeroinflation(combo_aggression_res_attack_sl_nb_mm)
check_overdispersion(combo_aggression_res_attack_sl_nb_mm)
check_singularity(combo_aggression_res_attack_sl_nb_mm)
confint(combo_aggression_res_attack_sl_nb_mm, level = 0.95, method = "profile")
# Ok - best model fit

# Poisson
combo_aggression_res_attack_sl_poi_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"))
summary(combo_aggression_res_attack_sl_poi_mm)
performance::check_zeroinflation(combo_aggression_res_attack_sl_poi_mm)
check_overdispersion(combo_aggression_res_attack_sl_poi_mm)
check_singularity(combo_aggression_res_attack_sl_poi_mm)
# Zero inflated

# Zi neg bin
combo_aggression_res_attack_sl_nb_zi_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_res_attack_sl_nb_zi_mm)
performance::check_zeroinflation(combo_aggression_res_attack_sl_nb_zi_mm)
check_overdispersion(combo_aggression_res_attack_sl_nb_zi_mm)
check_singularity(combo_aggression_res_attack_sl_nb_zi_mm)
# Not converging

# Zi poisson
combo_aggression_res_attack_sl_poi_zi_mm <- glmmTMB(Aggression_res_attack_approach ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"), zi = ~ 1 + Total_nr_display)
summary(combo_aggression_res_attack_sl_poi_zi_mm)
performance::check_zeroinflation(combo_aggression_res_attack_sl_poi_zi_mm)
check_overdispersion(combo_aggression_res_attack_sl_poi_zi_mm)
check_singularity(combo_aggression_res_attack_sl_poi_zi_mm)
# Ok but no Total_nr_display effect in the zi part


anova(combo_aggression_res_attack_sl_nb_mm, combo_aggression_res_attack_sl_poi_zi_mm)

## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_aggression_res_attack_sl_nb_mm)

# Plot residuals
plot(sim_res)
# Ok

testDispersion(sim_res)
# Ok

```


## III/2c. Duration of fights


```{r Duration of fights}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")

## Date distribution tests on raw data

hist(Group_period_sum$Fight_dur_s)

Group_period_sum2 <- Group_period_sum %>% filter(Fight_dur_s != 0)

hist(Group_period_sum2$Fight_dur_s)

library(fitdistrplus)
descdist(Group_period_sum2$Fight_dur_s, boot = 1000)
# No good


# Log-transformed data
descdist(log(Group_period_sum2$Fight_dur_s), boot = 1000)
hist(log(Group_period_sum$Fight_dur_s))
# Looks normal like


# Square root trasformation to avoid negative values
descdist(sqrt(Group_period_sum2$Fight_dur_s), boot = 1000)
hist(sqrt(Group_period_sum$Fight_dur_s))


Group_period_sum2$Fight_dur_s_tr <- ifelse(Group_period_sum2$Fight_dur_s == 0, 0, sqrt(Group_period_sum2$Fight_dur_s))

normal_dist <- fitdist(Group_period_sum2$Fight_dur_s_tr, "norm")
plot(normal_dist)

lognormal_dist <- fitdist(Group_period_sum2$Fight_dur_s_tr, "lnorm")
plot(lognormal_dist)

weibull_dist <- fitdist(Group_period_sum2$Fight_dur_s_tr, "weibull")
plot(weibull_dist)

gamma_dist <- fitdist(Group_period_sum2$Fight_dur_s_tr, "gamma")
plot(gamma_dist)

plot.legend <- c("normal", "lognormal", "weibull", "gamma_dist")
denscomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
qqcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
cdfcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)
ppcomp(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), legendtext = plot.legend)

gofstat(list(normal_dist,lognormal_dist,weibull_dist,gamma_dist), fitnames = c("normal", "lognormal", "weibull", "gamma_dist"))

plotdist(log(Group_period_sum2$Fight_dur_s_tr), histo = TRUE, demp = TRUE)

# gamma seems the best on the sqrt transformed data


Group_period_sum$Fight_dur_s_tr <- ifelse(Group_period_sum$Fight_dur_s == 0, 0, sqrt(Group_period_sum$Fight_dur_s))


## Model 1: Only intercept models - Random variable has no effect

# Gaussian
combo_figth_dur_lm2 <- glmmTMB(Fight_dur_s_tr ~  Condition + Week + Total_nr_display , data = Group_period_sum)
summary(combo_figth_dur_lm2)
# Random variable has no effect

# Gamma hurdle
combo_figth_dur_mm_gamma <- glmmTMB(Fight_dur_s_tr ~  Condition + Week + Total_nr_display , data = Group_period_sum, family = ziGamma(link="log"), ziformula = ~ 1 + Total_nr_display)
summary(combo_figth_dur_mm_gamma)
check_overdispersion(combo_figth_dur_mm_gamma)
confint(combo_figth_dur_mm_gamma, level = 0.95, method = "profile")
# Ok - final model

# Lognorm hurdle
combo_figth_dur_mm_lnorm <- glmmTMB(Fight_dur_s_tr ~  Condition + Week + Total_nr_display, data = Group_period_sum,family = glmmTMB::lognormal(link="log"),  ziformula = ~ Total_nr_display)
summary(combo_figth_dur_mm_lnorm)
check_overdispersion(combo_figth_dur_mm_lnorm)
# Ok

anova(combo_figth_dur_mm_gamma, combo_figth_dur_mm_lnorm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_figth_dur_mm_gamma)

# Plot residuals
plot(sim_res)
# Ok

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope)

# Gaussian
combo_figth_dur_sl_lm2 <- glmmTMB(Fight_dur_s_tr ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code) , data = Group_period_sum)
summary(combo_figth_dur_sl_lm2)
# No 


# Gamma hurdle
combo_figth_dur_sl_mm_gamma <- glmmTMB(Fight_dur_s_tr ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code) , data = Group_period_sum, family = ziGamma(link="log"), ziformula = ~ Total_nr_display)
summary(combo_figth_dur_sl_mm_gamma)
check_overdispersion(combo_figth_dur_sl_mm_gamma)
# Convergence problem with slope


combo_figth_dur_sl_mm_lnorm <- glmmTMB(Fight_dur_s_tr ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code) , data = Group_period_sum,family = glmmTMB::lognormal(link="log"),  ziformula = ~ Total_nr_display)
summary(combo_figth_dur_sl_mm_lnorm)
check_overdispersion(combo_figth_dur_sl_mm_lnorm)
# With slope it's not converging



## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_figth_dur_sl_mm_gamma)

# Plot residuals
plot(sim_res)
# Ok

testDispersion(sim_res)
# Ok


```


## III/2d. Number of chases against non-Residents


```{r Number of chases against non-Residents}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")


# Creating a uniform variable for the non-Residents
Group_period_sum$Chasings_marg_sat <- Group_period_sum$Chasings_marg + Group_period_sum$Chasings_sat


## Model 1: Only intercept models - Random variable has no effect

# Gaussian
combo_aggression_total_lm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_aggression_total_lm)

# Neg bin
combo_aggression_total_nb_mm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_total_nb_mm)
performance::check_zeroinflation(combo_aggression_total_nb_mm)
check_overdispersion(combo_aggression_total_nb_mm)
check_singularity(combo_aggression_total_nb_mm)
# Ok

# Poisson
combo_aggression_total_poi_mm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"))
summary(combo_aggression_total_poi_mm)
performance::check_zeroinflation(combo_aggression_total_poi_mm)
check_overdispersion(combo_aggression_total_poi_mm)
check_singularity(combo_aggression_total_poi_mm)
# Zero-inflated, over dispersed

# zi neg bin
combo_aggression_total_nb_zi_mm <- glmmTMB(Chasings_marg_sat ~ Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_total_nb_zi_mm)
performance::check_zeroinflation(combo_aggression_total_nb_zi_mm)
check_overdispersion(combo_aggression_total_nb_zi_mm)
check_singularity(combo_aggression_total_nb_zi_mm)
confint(combo_aggression_total_nb_zi_mm, level = 0.95, method = "profile")
# Ok - final model

anova(combo_aggression_total_nb_mm ,combo_aggression_total_nb_zi_mm)

## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_aggression_total_nb_zi_mm)

# Plot residuals
plot(sim_res)
# Ok - some deviation a the lower quartile

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope) - slope has very little effect

# Gaussian
combo_chasings_total_sl_lm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_chasings_total_sl_lm)

# Neg bin
combo_chasings_total_sl_nb_mm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_chasings_total_sl_nb_mm)
performance::check_zeroinflation(combo_chasings_total_sl_nb_mm)
check_overdispersion(combo_chasings_total_sl_nb_mm)
check_singularity(combo_chasings_total_sl_nb_mm)
# Convergence problem with slope

# Poisson
combo_chasings_total_sl_poi_mm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"))
summary(combo_chasings_total_sl_poi_mm)
performance::check_zeroinflation(combo_chasings_total_sl_poi_mm)
check_overdispersion(combo_chasings_total_sl_poi_mm)
check_singularity(combo_chasings_total_sl_poi_mm)
# Zero-inflated

# zi neg bin
combo_chasings_total_sl_nb_zi_mm <- glmmTMB(Chasings_marg_sat ~ Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_chasings_total_sl_nb_zi_mm)
performance::check_zeroinflation(combo_chasings_total_sl_nb_zi_mm)
check_overdispersion(combo_chasings_total_sl_nb_zi_mm)
check_singularity(combo_chasings_total_sl_nb_zi_mm)
# Ok 

# Zi poisson
combo_chasings_total_sl_poi_zi_mm <- glmmTMB(Chasings_marg_sat ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~ 1 + Total_nr_display)
summary(combo_chasings_total_sl_poi_zi_mm)
performance::check_zeroinflation(combo_chasings_total_sl_poi_zi_mm)
check_overdispersion(combo_chasings_total_sl_poi_zi_mm)
check_singularity(combo_chasings_total_sl_poi_zi_mm)
confint(combo_chasings_total_sl_poi_zi_mm, level = 0.95)
# Ok - final model

anova(combo_chasings_total_sl_nb_zi_mm, combo_chasings_total_sl_poi_zi_mm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_chasings_total_sl_nb_zi_mm)

# Plot residuals
plot(sim_res)
# Ok - some deviation a the lower quartile

testDispersion(sim_res)
# Ok

```


## III/2e. Number of attacks against non-Residents


```{r Number of attacks against non-Residents }

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")

# Creating a uniform variable for the non-Residents
Group_period_sum$Attacks_marg_sat <- Group_period_sum$Attacks_sat + Group_period_sum$Attacks_marg


## Model 1: Only intercept models

# Gaussian
combo_aggression_total_lm <- glmmTMB(Attacks_marg_sat ~  Condition + Week + Total_nr_display + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_aggression_total_lm)

# Neg bin
combo_aggression_total_nb_mm <- glmmTMB(Attacks_marg_sat ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_total_nb_mm)
performance::check_zeroinflation(combo_aggression_total_nb_mm)
check_overdispersion(combo_aggression_total_nb_mm)
check_singularity(combo_aggression_total_nb_mm)
# Ok 

# Poisson
combo_aggression_total_poi_mm <- glmmTMB(Attacks_marg_sat ~  Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"))
summary(combo_aggression_total_poi_mm)
performance::check_zeroinflation(combo_aggression_total_poi_mm)
check_overdispersion(combo_aggression_total_poi_mm)
check_singularity(combo_aggression_total_poi_mm)
confint(combo_aggression_total_poi_mm, level = 0.95, method = "profile")
# Ok - final model

# zi neg bin
combo_aggression_total_nb_zi_mm <- glmmTMB(Attacks_marg_sat ~ Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_total_nb_zi_mm)
performance::check_zeroinflation(combo_aggression_total_nb_zi_mm)
check_overdispersion(combo_aggression_total_nb_zi_mm)
check_singularity(combo_aggression_total_nb_zi_mm)
# Ok

# zi Poisson
combo_aggression_total_poi_zi_mm <- glmmTMB(Attacks_marg_sat ~ Condition + Week + Total_nr_display  + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"), zi = ~ 1 + Total_nr_display)
summary(combo_aggression_total_poi_zi_mm)
performance::check_zeroinflation(combo_aggression_total_poi_zi_mm)
check_overdispersion(combo_aggression_total_poi_zi_mm)
check_singularity(combo_aggression_total_poi_zi_mm)
# Ok

anova(combo_aggression_total_nb_mm, combo_aggression_total_poi_mm, combo_aggression_total_nb_zi_mm, combo_aggression_total_poi_zi_mm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_aggression_total_poi_mm)

# Plot residuals
plot(sim_res)
# Ok - some deviation a the lower quartile

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope) - slope has very little effect

# Gaussian
combo_aggression_total_sl_lm <- glmmTMB(Attacks_marg_sat ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_aggression_total_sl_lm)


# Neg bin
combo_aggression_total_sl_nb_mm <- glmmTMB(Attacks_marg_sat ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2)
summary(combo_aggression_total_sl_nb_mm)
performance::check_zeroinflation(combo_aggression_total_sl_nb_mm)
check_overdispersion(combo_aggression_total_sl_nb_mm)
check_singularity(combo_aggression_total_sl_nb_mm)
confint(combo_aggression_total_sl_nb_mm, level = 0.95)
# Ok

# Poisson
combo_aggression_total_sl_poi_mm <- glmmTMB(Attacks_marg_sat ~  Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"))
summary(combo_aggression_total_sl_poi_mm)
performance::check_zeroinflation(combo_aggression_total_sl_poi_mm)
check_overdispersion(combo_aggression_total_sl_poi_mm)
check_singularity(combo_aggression_total_sl_poi_mm)
# Ok - final model

# zi neg bin
combo_aggression_total_sl_nb_zi_mm <- glmmTMB(Attacks_marg_sat ~ Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~ 1 + Total_nr_display)
summary(combo_aggression_total_sl_nb_zi_mm)
performance::check_zeroinflation(combo_aggression_total_sl_nb_zi_mm)
check_overdispersion(combo_aggression_total_sl_nb_zi_mm)
check_singularity(combo_aggression_total_sl_nb_zi_mm)
# Zi part does not converge

# zi poisson
combo_aggression_total_sl_poi_zi_mm <- glmmTMB(Attacks_marg_sat ~ Condition + Week + Total_nr_display  + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = "log"), zi = ~ 1 + Total_nr_display)
summary(combo_aggression_total_sl_poi_zi_mm)
performance::check_zeroinflation(combo_aggression_total_sl_poi_zi_mm)
check_overdispersion(combo_aggression_total_sl_poi_zi_mm)
check_singularity(combo_aggression_total_sl_poi_zi_mm)
# Zi part does not converge

anova(combo_aggression_total_sl_nb_mm, combo_aggression_total_sl_poi_mm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_aggression_total_sl_poi_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok



```


## III/3. Female mate choice 


# Probability of female visits (a), copulation attempts (b) and successful copulations (c) for a Resident over a group period

```{r Probability of female choice models}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")

# Visits

Group_period_sum <- Group_period_sum %>% mutate(Visit_occurrence_week = if_else(Visit_occurrence > 0, 1, 0)) %>% relocate(Visit_occurrence_week, .after = Visit_occurrence) %>% group_by(Combo_lek_week, Colour_code) %>% mutate(Co_displ_occurrence2 = sum(Co_displ_occurrence)) %>% relocate(Co_displ_occurrence2, .after = Co_displ_occurrence) %>% mutate(Co_displ_occurrence2 = if_else(Co_displ_occurrence2 >0, 1, 0))

Combo_vis_occ_log_reg <- glmer(Visit_occurrence_week ~ Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), family = "binomial", data = Group_period_sum)
summary(Combo_vis_occ_log_reg)
confint(Combo_vis_occ_log_reg, level = 0.95, method = "profile")

sum(Group_period_sum$Visit_occurrence_week[Group_period_sum$Condition == "Satellite"]) # 26/60
sum(Group_period_sum$Visit_occurrence_week[Group_period_sum$Condition == "Marginal"]) # 16/60


# Copulation attempts

Group_period_sum <- Group_period_sum %>% mutate(Copulation_occurrence_week = if_else(Copulation_occurrence > 0, 1, 0)) %>% relocate(Copulation_occurrence_week, .after = Copulation_occurrence) %>% group_by(Combo_lek_week, Colour_code) %>% mutate(Co_displ_occurrence2 = sum(Co_displ_occurrence)) %>% relocate(Co_displ_occurrence2, .after = Co_displ_occurrence) %>% mutate(Co_displ_occurrence2 = if_else(Co_displ_occurrence2 >0, 1, 0))

Comb_cop_occ_log_reg <- glmer(Copulation_occurrence_week ~ Condition + Week + Total_nr_display + (1|Combo_lek_week:Colour_code), family = "binomial", data = Group_period_sum)
confint(Comb_cop_occ_log_reg)
summary(Comb_cop_occ_log_reg)

sum(Group_period_sum$Copulation_occurrence_week[Group_period_sum$Condition == "Satellite"]) # 14/60
sum(Group_period_sum$Copulation_occurrence_week[Group_period_sum$Condition == "Marginal"]) # 14/60


## Successful copulation occurrence per male per week

Group_period_sum <- Group_period_sum %>% mutate(Copulation_occurrence_successful_week = if_else(Copulation_occurrence_successful > 0, 1, 0)) %>% relocate(Copulation_occurrence_successful_week, .after = Copulation_occurrence_successful) %>% group_by(Combo_lek_week, Colour_code) %>% mutate(Co_displ_occurrence2 = sum(Co_displ_occurrence)) %>% relocate(Co_displ_occurrence2, .after = Co_displ_occurrence) %>% mutate(Co_displ_occurrence2 = if_else(Co_displ_occurrence2 >0, 1, 0))


Combos_suc_cop_occ_log_reg <- glm(Copulation_occurrence_successful_week ~ Condition + Week + Total_nr_display, family = "binomial", data = Group_period_sum)
summary(Combos_suc_cop_occ_log_reg)
confint(Combos_suc_cop_occ_log_reg)




```




# III/3a. Total number of female visits

```{r Total number of female visits}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")

## Model1 - intercept only

# Gaussian
combo_visit_nr_lm_m2 <- glmmTMB(Total_visit_nr_all_females ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_visit_nr_lm_m2)


# Neg bin
combo_visit_nr_nb_m2 <- glmmTMB(Total_visit_nr_all_females ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  0)
summary(combo_visit_nr_nb_m2)
performance::check_zeroinflation(combo_visit_nr_nb_m2)
check_overdispersion(combo_visit_nr_nb_m2)
check_singularity(combo_visit_nr_nb_m2)
# Ok

# Poisson
combo_visit_nr_poi_m2 <- glmmTMB(Total_visit_nr_all_females ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  0)
summary(combo_visit_nr_poi_m2)
performance::check_zeroinflation(combo_visit_nr_poi_m2)
check_overdispersion(combo_visit_nr_poi_m2)
check_singularity(combo_visit_nr_poi_m2)
# Zero-inflated, over dispersed


# Zero_inflated neg bin
combo_visit_nr_zi_mm <- glmmTMB(Total_visit_nr_all_females ~  Total_nr_display + Condition + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1 + Total_nr_display)
summary(combo_visit_nr_zi_mm)
performance::check_zeroinflation(combo_visit_nr_zi_mm)
check_overdispersion(combo_visit_nr_zi_mm)
check_singularity(combo_visit_nr_zi_mm)
confint(combo_visit_nr_zi_mm, level = 0.95, method = "profile")
# Ok - final model

anova(combo_visit_nr_nb_m2, combo_visit_nr_zi_mm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_visit_nr_zi_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok



## Model 2: intercept/slope models (with condition as slope)

# Gaussian
combo_visit_nr_sl_lm_mm <- glmmTMB(Total_visit_nr_all_females ~  Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_visit_nr_sl_lm_mm)


# Neg bin
combo_visit_nr_sl_mm <- glmmTMB(Total_visit_nr_all_females ~  Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  0)
summary(combo_visit_nr_sl_mm)
performance::check_zeroinflation(combo_visit_nr_sl_mm)
check_overdispersion(combo_visit_nr_sl_mm)
check_singularity(combo_visit_nr_sl_mm)
# Ok

# Poisson
combo_visit_nr_poi_sl_mm <- glmmTMB(Total_visit_nr_all_females ~ Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = poisson(link = log))
summary(combo_visit_nr_poi_sl_mm)
performance::check_zeroinflation(combo_visit_nr_poi_sl_mm, tolerance = 0.05)
check_overdispersion(combo_visit_nr_poi_sl_mm)
check_singularity(combo_visit_nr_poi_sl_mm)
# Zero inflated


# Zi Poisson
combo_visit_nr_zi_sl_poi_mm <- glmmTMB(Total_visit_nr_all_females ~  Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  1 )
summary(combo_visit_nr_zi_sl_poi_mm)
performance::check_zeroinflation(combo_visit_nr_zi_sl_poi_mm)
check_overdispersion(combo_visit_nr_zi_sl_poi_mm)
check_singularity(combo_visit_nr_zi_sl_poi_mm)
confint(combo_visit_nr_zi_sl_poi_mm, level = 0.95)
# Ok final model

# Zi neg bin
combo_visit_nr_zi_sl_nb_mm <- glmmTMB(Total_visit_nr_all_females ~  Condition + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1 + Total_nr_display)
summary(combo_visit_nr_zi_sl_nb_mm)
performance::check_zeroinflation(combo_visit_nr_zi_sl_nb_mm)
check_overdispersion(combo_visit_nr_zi_sl_nb_mm)
check_singularity(combo_visit_nr_zi_sl_nb_mm)
# Not converging


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_visit_nr_zi_sl_poi_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok


```


# III/3b. Total duration of female visits


```{r Total duration of female visits}

Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")


## Distribution test

# Gamma distribution on the non-zero values

hist(Group_period_sum$Total_visit_duration_all_females)

Group_period_sum2 <- Group_period_sum %>% filter(Total_visit_duration_all_females != 0)

hist(Group_period_sum2$Total_visit_duration_all_females)

library(fitdistrplus)
descdist(Group_period_sum2$Total_visit_duration_all_females, discrete = FALSE, boot = 1000)
plotdist(Group_period_sum2$Total_visit_duration_all_females, histo = TRUE, demp = TRUE)

norm <- fitdist(Group_period_sum2$Total_visit_duration_all_females, "norm")
plot(norm)

lognormal <- fitdist(Group_period_sum2$Total_visit_duration_all_females, "lnorm")
plot(lognormal)

gamma <- fitdist(Group_period_sum2$Total_visit_duration_all_females, "gamma")
plot(gamma)

plot.legend <- c("norm", "lognormal", "gamma")
denscomp(list(norm, lognormal, gamma), legendtext = plot.legend)
qqcomp(list(norm, lognormal, gamma), legendtext = plot.legend)
cdfcomp(list(norm, lognormal, gamma), legendtext = plot.legend)
ppcomp(list(norm, lognormal, gamma), legendtext = plot.legend)

gofstat(list(norm, lognormal_dist, gamma), fitnames = c("normal", "log-Normal", "Gamma"))

# Log transform
Group_period_sum2$Total_visit_duration_all_females_tr <- log(Group_period_sum2$Total_visit_duration_all_females)

hist(Group_period_sum2$Total_visit_duration_all_females_tr)


# Square-root transform
Group_period_sum2$Total_visit_duration_all_females_tr <- sqrt(Group_period_sum2$Total_visit_duration_all_females)

hist(Group_period_sum2$Total_visit_duration_all_females_tr)

descdist(Group_period_sum2$Total_visit_duration_all_females_tr, discrete = FALSE, boot = 1000)
plotdist(Group_period_sum2$Total_visit_duration_all_females_tr, histo = TRUE, demp = TRUE)

norm <- fitdist(Group_period_sum2$Total_visit_duration_all_females_tr, "norm")
plot(norm)

lognormal <- fitdist(Group_period_sum2$Total_visit_duration_all_females_tr, "lnorm")
plot(lognormal)

gamma <- fitdist(Group_period_sum2$Total_visit_duration_all_females_tr, "gamma")
plot(gamma)

plot.legend <- c("norm", "lognormal", "gamma")
denscomp(list(norm, lognormal, gamma), legendtext = plot.legend)
qqcomp(list(norm, lognormal, gamma), legendtext = plot.legend)
cdfcomp(list(norm, lognormal, gamma), legendtext = plot.legend)
ppcomp(list(norm, lognormal, gamma), legendtext = plot.legend)

gofstat(list(norm, lognormal, gamma), fitnames = c("normal", "log-Normal", "Gamma"))
# Gamma is the best on the sqrt transformad data



## Model1 - intercept only

Group_period_sum$Total_visit_duration_all_females_tr <- ifelse(Group_period_sum$Total_visit_duration_all_females == 0, 0, sqrt(Group_period_sum$Total_visit_duration_all_females))


# Gamma hurdle gamma model
combo_visit_dur_gamma_hurdle_mm <- glmmTMB(Total_visit_duration_all_females_tr ~ Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum, family = ziGamma(link="log"), ziformula = ~ 1 + Total_nr_display)
summary(combo_visit_dur_gamma_hurdle_mm)
check_overdispersion(combo_visit_dur_gamma_hurdle_mm)
confint(combo_visit_dur_gamma_hurdle_mm, level = 0.95, method = "profile")
# Ok

# Lognorm hurdle model
combo_visit_dur_lognorm_hurdle_mm <- glmmTMB(Total_visit_duration_all_females_tr ~ Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum, family = glmmTMB::lognormal(link="log"), ziformula = ~ 1 + Total_nr_display)
summary(combo_visit_dur_lognorm_hurdle_mm)
check_overdispersion(combo_visit_dur_lognorm_hurdle_mm)
# Final model

anova(combo_visit_dur_gamma_hurdle_mm, combo_visit_dur_lognorm_hurdle_mm)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_visit_dur_lognorm_hurdle_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope)

# Transformed data does not converge
combo_visit_dur_gamma_hurdle_sl_mm <- glmmTMB(Total_visit_duration_all_females ~ Condition + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = ziGamma(link="log"), ziformula = ~ 1 + Total_nr_display)
summary(combo_visit_dur_gamma_hurdle_sl_mm)
check_overdispersion(combo_visit_dur_gamma_hurdle_sl_mm)
confint(combo_visit_dur_gamma_hurdle_sl_mm, level = 0.95, method = "profile")
# Ok - final model

combo_visit_dur_lognorm_hurdle_sl_mm <- glmmTMB(Total_visit_duration_all_females ~ Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = glmmTMB::lognormal(link="log"), ziformula = ~ 1 + Total_nr_display)
summary(combo_visit_dur_lognorm_hurdle_sl_mm)
check_overdispersion(combo_visit_dur_lognorm_hurdle_sl_mm)
# Slope doesn't converge


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_visit_dur_gamma_hurdle_sl_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok

```


# III/3c. Number of copulation attempts


```{r Copulation attempts}


Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")


## Model1: intercept only models

# Gaussian
combo_cop_nr_lm_mm <- glmmTMB(Copulation_nr ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_cop_nr_lm_mm)


# Neg bin
combo_cop_nr_mm <- glmmTMB(Copulation_nr ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  0)
summary(combo_cop_nr_mm)
performance::check_zeroinflation(combo_cop_nr_mm)
check_overdispersion(combo_cop_nr_mm)
check_singularity(combo_cop_nr_mm)
# Ok


# Poisson model
combo_cop_nr_poi_mm <- glmer(Copulation_nr ~ Condition  + Total_nr_display + Week + (1|Combo_lek_week/Colour_code), data = Group_period_sum, family = poisson(link = log))
summary(combo_cop_nr_poi_mm)
performance::check_zeroinflation(combo_cop_nr_poi_mm, tolerance = 0.05)
check_overdispersion(combo_cop_nr_poi_mm)
# Zero inflated


# Neg bin zi
combo_cop_nr__nb_zi_mm <- glmmTMB(Copulation_nr ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1 + Total_nr_display)
summary(combo_cop_nr__nb_zi_mm)
performance::check_zeroinflation(combo_cop_nr__nb_zi_mm)
check_overdispersion(combo_cop_nr__nb_zi_mm)
check_singularity(combo_cop_nr__nb_zi_mm)
confint(combo_cop_nr__nb_zi_mm, level = 0.95, method = "profile")
# Ok, Final model!


# Poisson zi
combo_cop_nr_poi_zi_mm <- glmmTMB(Copulation_nr ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  1 + Total_nr_display)
summary(combo_cop_nr_poi_zi_mm)
performance::check_zeroinflation(combo_cop_nr_poi_zi_mm)
check_overdispersion(combo_cop_nr_poi_zi_mm)
check_singularity(combo_cop_nr_poi_zi_mm)
# Ok

anova(combo_cop_nr_mm, combo_cop_nr__nb_zi_mm, combo_cop_nr_poi_zi_mm)


# Model comparison
cand.set <- list(combo_cop_nr_lm_mm, combo_cop_nr_mm, combo_cop_nr__nb_zi_mm, combo_cop_nr_poi_zi_mm)
names <- c("m_lm", "m_nb", "m_nb_zi", "m_p_zi")
aictab(cand.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_cop_nr__nb_zi_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok



## Model 2: intercept/slope models (with condition as slope)

# Gaussian
combo_cop_nr_sl_lm_mm <- glmmTMB(Copulation_nr ~ Condition + Total_nr_display + Week  +(Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_cop_nr_sl_lm_mm)
# Convergence


# Neg bin
combo_cop_nr_sl_mm <- glmmTMB(Copulation_nr ~ Condition + Total_nr_display + Week  +(Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = nbinom2)
summary(combo_cop_nr_sl_mm)
performance::check_zeroinflation(combo_cop_nr_sl_mm, tolerance = 0.05)
check_overdispersion(combo_cop_nr_sl_mm)
check_singularity(combo_cop_nr_sl_mm)
# No Zero inflated BUT Warning: iteration limit reached

# zi neg bin
combo_cop_nr_zi_sl_nb_mm <- glmmTMB(Copulation_nr ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1 + Total_nr_display)
summary(combo_cop_nr_zi_sl_nb_mm)
performance::check_zeroinflation(combo_cop_nr_zi_sl_nb_mm)
check_overdispersion(combo_cop_nr_zi_sl_nb_mm)
check_singularity(combo_cop_nr_zi_sl_nb_mm)
# Ok but the random structure


# Poisson
combo_cop_nr_sl_mm <- glmmTMB(Copulation_nr ~ Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = poisson(link = log))
summary(combo_cop_nr_sl_mm)
performance::check_zeroinflation(combo_cop_nr_sl_mm, tolerance = 0.05)
check_overdispersion(combo_cop_nr_sl_mm)
check_singularity(combo_cop_nr_sl_mm)
confint(combo_cop_nr_sl_mm, level = 0.95, method = "profile")
# Ok - final model

# Zi poisson
combo_cop_nr_zi_sl_poi_mm <- glmmTMB(Copulation_nr ~  Condition + Total_nr_display  + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  1 + Total_nr_display )
summary(combo_cop_nr_zi_sl_poi_mm)
performance::check_zeroinflation(combo_cop_nr_zi_sl_poi_mm)
check_overdispersion(combo_cop_nr_zi_sl_poi_mm)
check_singularity(combo_cop_nr_zi_sl_poi_mm)
# Convergence

combo_cop_nr_zi_sl_poi_mm2 <- glmmTMB(Copulation_nr ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  1 )
summary(combo_cop_nr_zi_sl_poi_mm2)
performance::check_zeroinflation(combo_cop_nr_zi_sl_poi_mm2)
check_overdispersion(combo_cop_nr_zi_sl_poi_mm2)
check_singularity(combo_cop_nr_zi_sl_poi_mm2)
# Ok

anova(combo_cop_nr_zi_sl_nb_mm, combo_cop_nr_sl_mm,  combo_cop_nr_zi_sl_poi_mm2)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_cop_nr_sl_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok


```


# III/3d. Number of successful copulations


```{r Successful copulations}


Group_period_sum <- read.csv("Resident cooperation MS Kupan Data/Group_period_sums.csv")


## Model1: intercept only models

# Gaussian
combo_suc_cop_nr_lm_mm <- glmmTMB(Total_successful_copulations ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_suc_cop_nr_lm_mm)
# Ok

# Neg bin
combo_suc_cop_nr_nb_mm <- glmmTMB(Total_successful_copulations ~  Condition + Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  0)
summary(combo_suc_cop_nr_nb_mm)
performance::check_zeroinflation(combo_suc_cop_nr_nb_mm)
check_overdispersion(combo_suc_cop_nr_nb_mm)
check_singularity(combo_suc_cop_nr_nb_mm)
# Ok

# Poisson
combo_suc_cop_nr_poi_mm <- glmer(Total_successful_copulations ~ Condition  +  Total_nr_display + Week + (1|Combo_lek_week:Colour_code), data = Group_period_sum, family = poisson(link = log))
summary(combo_suc_cop_nr_poi_mm)
performance::check_zeroinflation(combo_suc_cop_nr_poi_mm, tolerance = 0.05)
check_overdispersion(combo_suc_cop_nr_poi_mm)
check_singularity(combo_suc_cop_nr_poi_mm)
# Zero inflated


# Neg bin zero inflated
combo_suc_cop_nr_zi_mm <- glmmTMB(Total_successful_copulations ~  Condition   + Week +  Total_nr_display + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1 + Total_nr_display)
summary(combo_suc_cop_nr_zi_mm)
performance::check_zeroinflation(combo_suc_cop_nr_zi_mm)
check_overdispersion(combo_suc_cop_nr_zi_mm)
check_singularity(combo_suc_cop_nr_zi_mm)
# Ok

# Zi Poisson
combo_suc_cop_poi_zi_mm <- glmmTMB(Total_successful_copulations ~  Condition   + Week +  Total_nr_display + (1|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  1 + Total_nr_display)
summary(combo_suc_cop_poi_zi_mm)
performance::check_zeroinflation(combo_suc_cop_poi_zi_mm)
check_overdispersion(combo_suc_cop_poi_zi_mm)
check_singularity(combo_suc_cop_poi_zi_mm)
confint(combo_suc_cop_nr_zi_mm, level = 0.95, method = "profile")
# OK - final model

anova(combo_suc_cop_nr_nb_mm, combo_suc_cop_nr_zi_mm, combo_suc_cop_poi_zi_mm)


# Model comparison
cand.set <- list(combo_suc_cop_nr_nb_mm, combo_suc_cop_nr_zi_mm, combo_suc_cop_poi_zi_mm )
names <- c("m_nb", "m_zi_nb", "m_zi_poi")
aictab(cand.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)


## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_suc_cop_poi_zi_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok


## Model 2: intercept/slope models (with condition as slope)

# Gaussian
combo_suc_cop_nr_sl_lm_mm <- glmmTMB(Total_successful_copulations ~ Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum)
summary(combo_suc_cop_nr_sl_lm_mm)
# Ok

# Neg bin
combo_suc_cop_nr_sl_mm <- glmmTMB(Total_successful_copulations ~ Condition + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = nbinom2)
summary(combo_suc_cop_nr_sl_mm)
performance::check_zeroinflation(combo_suc_cop_nr_sl_mm, tolerance = 0.05)
check_overdispersion(combo_suc_cop_nr_sl_mm)
check_singularity(combo_suc_cop_nr_sl_mm)
# Ok

# Poisson
combo_cop_nr_poi_sl_mm <- glmmTMB(Total_successful_copulations ~ Condition  + Total_nr_display + Week + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum, family = poisson(link = log))
summary(combo_cop_nr_poi_sl_mm)
performance::check_zeroinflation(combo_cop_nr_poi_sl_mm, tolerance = 0.05)
check_overdispersion(combo_cop_nr_poi_sl_mm)
check_singularity(combo_cop_nr_poi_sl_mm)
# Ok

# Zi neg bin
combo_suc_cop_nr_sl_zi_nb_mm <- glmmTMB(Total_successful_copulations ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1 + Total_nr_display)
summary(combo_suc_cop_nr_sl_zi_nb_mm)
performance::check_zeroinflation(combo_suc_cop_nr_sl_zi_nb_mm)
check_overdispersion(combo_suc_cop_nr_sl_zi_nb_mm)
check_singularity(combo_suc_cop_nr_sl_zi_nb_mm)
# Convergence

# Zi neg bin
combo_suc_cop_nr_sl_zi_nb_mm2 <- glmmTMB(Total_successful_copulations ~  Condition + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = nbinom2, zi = ~  1)
summary(combo_suc_cop_nr_sl_zi_nb_mm2)
performance::check_zeroinflation(combo_suc_cop_nr_sl_zi_nb_mm2)
check_overdispersion(combo_suc_cop_nr_sl_zi_nb_mm2)
check_singularity(combo_suc_cop_nr_sl_zi_nb_mm2)
# Ok

# Zi Poisson
combo_suc_cop_nr_sl_zi_poi_mm <- glmmTMB(Total_successful_copulations ~  Condition  + Week + Total_nr_display + (Condition|Combo_lek_week:Colour_code), data = Group_period_sum,  family = poisson(link = log), zi = ~  1 )
summary(combo_suc_cop_nr_sl_zi_poi_mm)
performance::check_zeroinflation(combo_suc_cop_nr_sl_zi_poi_mm)
check_overdispersion(combo_suc_cop_nr_sl_zi_poi_mm)
check_singularity(combo_suc_cop_nr_sl_zi_poi_mm)
confint(combo_suc_cop_nr_sl_zi_poi_mm, level = 0.95) # with method = profile it's not converging
# Ok, convergence problem with Total_nr_display in zi part, final model

anova(combo_suc_cop_nr_sl_mm, combo_cop_nr_poi_sl_mm, combo_suc_cop_nr_sl_zi_nb_mm2, combo_suc_cop_nr_sl_zi_poi_mm)

# Model comparison
cand.set <- list(combo_cop_nr_poi_sl_mm, combo_suc_cop_nr_sl_zi_nb_mm, combo_suc_cop_nr_sl_zi_poi_mm)
names <- c("m_poi", "m_zi_nb", "m_zi_poi")
aictab(cand.set, modnames=names, second.ord=TRUE, nobs=NULL, sort=TRUE)

## Model inspection

# Simulate residuals
sim_res <- simulateResiduals(fittedModel = combo_suc_cop_nr_sl_zi_poi_mm)

# Plot residuals
plot(sim_res)
# Ok 

testDispersion(sim_res)
# Ok


```


























